Challenging Fuel Cycle Modeling Assumptions: Facility and Time Step Discretization Effects

### 2016-02-05 paper.tex
address more comments

One of the major motivations for the development of the Cyclus fuel cycle
simulator \cite{cyclus_2015} was creating a simulation environment that is
more expressive than more traditional fuel cycle simulators.  Cyclus was
designed with a plug-in style architecture that allows different models for
facility types, known as \emph{archetypes}, to be swapped in and out easily.

@@

A single fuel cycle transition scenario is used with a few modeling variations
resulting in four different cases:

@@

Conducting this analysis involved developing some additional capability
in/around Cyclus.  Three primary pieces to the methodology are:

@@

A fleet reactor archetype was created for Cyclus.  Although the modeling of
individual, discrete facilities was a motivation for Cyclus, its flexibility
makes it relatively straightforward to create plug-in archetypes to model
anywhere along the spectrum from individual, discrete facilities to
continuous flow fleet facilities.  In order to contrast well with the individual,
single-facility granularity modeling that is part of the standard Cyclus archetypes, 
a fleet archetype was created for this work with aggregate facility behavior and
continuous flow.

@@

\begin{figure}[!h]
    \centering
    \includegraphics[keepaspectratio=true,width=0.45\textwidth,height=.9\textheight]{exp2/flow.eps}
    \caption[Material flow paths]{Potential material flow paths between facility types.}
    %% consider a Cyclist-derived visualization here?
    \label{fig:flow}
\end{figure}

@@

In each of the four cases, the initial 100 LWRs are modified to have a zero-length
refueling outage with an explicit 900 MWe net power output capacity.  Because the
individual reactor model does not have any way to start a reactor mid-cycle,
this was done to avoid having all initial LWRs refuel at the same time.  The
parameters for each case were also selected to keep capacity factors for
individual reactors very roughly around 90\%, although they are actually 
closer to 80\% due to integer variable constraints on the case MI and QI
reactor configuration.

Instead of annual deployments, a longer 21-month deployment period is used
because it provides better natural staggering for the reactor refueling
cycles. The same deployment schedule is used for all four cases; power
capacity is built along a curve starting at 100 GWe in year zero following the
1\% exponential growth curve.  This particular deployment schedule is chosen
because it causes significant fuel shortages providing interesting features to
investigate and compare.

>>>>

One of the major motivations for the development of the Cyclus fuel cycle
simulator \cite{cyclus_2015} was creating a simulation environment that is
more expressive than more traditional fuel cycle simulators.  Cyclus was
designed with a plug-in style architecture that allows different models for
facility types, known as \emph{archetypes}, to be swapped in and out easily.
While the reactor archetypes used in this analysis do not implement
internal physics calculations, plug-in archetypes such as Bright-lite
\cite{flanagan_bright-lite_2014} have been developed for Cyclus that provide
varying degrees modeling fidelity.
% response to technical comment 2.

@@

Two particular design choices are selected for investigation: time step
duration and facility discretization.  A single fuel cycle transition scenario
is run in a set of simulations using combinations of the time step duration
and facility discretization  --- four four different cases:

@@

%% response to technical comment 1.
These four cases span a spectrum of fidelity with one end being more realistic
(i.e. smaller time steps, individual facilities) and the other being more
appropriate for scoping studies (i.e.  larger time steps, fleet facilities).
Conducting this analysis involved developing some additional capability
in/around Cyclus.  Three primary pieces to the methodology are:

@@

A fleet reactor archetype was created for Cyclus.  Although the modeling of
individual, discrete facilities was a motivation for Cyclus, its flexibility
makes it relatively straightforward to create plug-in archetypes to model
anywhere along the spectrum from individual, discrete facilities to continuous
flow fleet facilities.  In order to contrast well with the individual,
single-facility granularity modeling that is part of the standard Cyclus
archetypes, a fleet archetype was created for this work with aggregate
facility behavior and continuous flow.  Although it would certainly be
interesting to compare many intermediate levels of facility discretization
(e.g. 1-reactor groups, 10-reactor groups, single-fleet, etc.), such a
detailed analysis is beyond the scope of this work.
% address technical comment 14

@@

\begin{figure}[!h]
    \centering
    \includegraphics[keepaspectratio=true,width=0.45\textwidth,height=.89\textheight]{exp2/flow.eps}
    \caption[Material flow paths]{
        Material flow paths between facility types. The DU source is separate
        from enrichment tails for modeling simplicity, although enrichment
        tails could be used for added realism.  The primary fissile isotope in
        the fissile separations stream is $_{239}Pu$.
    }
    % response to technical comment 9
    \label{fig:flow}
\end{figure}

@@

In each of the four cases, the initial 100 LWRs are modified to have a
zero-length refueling outage with an explicit 900 MWe net power output
capacity.  Because the individual reactor model does not have any way to start
a reactor mid-cycle, this is a modeling trick that was done to avoid having
all initial LWRs refuel at the same time.  This adjustment serves to improve
the realism associated with the effects being investigated (i.e. fleet-average
power generation) even though it is unrealistic in other ways.
% response to technical comment 11

The parameters for each case were also selected to keep capacity factors for
individual reactors very roughly around 90\%, although they are actually
closer to 80\% due to integer variable constraints on the case MI and QI
reactor configuration.

% response to technical comment 12
Instead of annual deployments, a longer 21-month deployment period is used
because it provides better natural staggering for the reactor refueling
cycles. The 630-month lowest common multiple (LCM) for 21-months (deployment
period), 15 months (SFR cycle), and 18 months (LWR cycle) is much larger than
the 180-month LCM when using a 12-month build period providing a more even
power generation profile.  The same deployment schedule is used for all four
cases; power capacity is built along a curve starting at 100 GWe in year zero
following the 1\% exponential growth curve.  Although many alternate
deployment schedules exist that avoid SFR fuel shortages (e.g. a more gradual
shift toward SFRs), this particular schedule is deliberately chosen because it
causes significant fuel shortages.  This is done in order to force the
simulation and facility models into more extreme circumstances in order to
expose behavioral differences among the design choices investigated.
% response to general comment paragraph
% response to technical comment 13
